The Surprising Runtime Fragility Found when Querying a Single Table

### 2015-04-27 testdata/chunked_column_layouts/draft.tex
!

>>>>

\begin{table}[!b] 
\pivotTable[width=0.478\textwidth, height=0.7478\textwidth, scale=0.666, rows={"Machine", "Table schema", "Query"}, aggregation=Bests, aggregationattribute=Query time]
{SELECT
m.cpuarchitecture 																													AS Machine,
IIF(d.tableschema = '(long a, long b)', 'long', IIF(d.tableschema = '(char a, char b)', 'char', IIF(d.tableschema = '(int a, int b)', 'int', 'n/a')))   			AS [Table schema],
IIF(q.querytext = 'SELECT MIN(a+b) FROM t', 'Q1', 'Q2')     																				AS [Query],
c.compiler      																														AS Compiler,
c.optlevel      																														AS [Opt. level],
l.name          																														AS [Layout name],
CAST(COALESCE(IIF(i.templateparam, 'C', 'R'), 'n/a') AS VARCHAR) 																		AS [Chunk size provided at],
runtimes																																AS [Query time]
  FROM (SELECT machineid, datasetid, queryid, compilerid, layoutid, implementationid, GRUBBS_FILTER(ARRAY(runtime)) as runtimes FROM fact_experiment GROUP BY machineid, datasetid, queryid, compilerid, layoutid, implementationid) AS v 
  JOIN dim_machine m ON m.id = v.machineid 
  JOIN dim_dataset d ON d.id = v.datasetid 
  JOIN dim_compiler c ON c.id = v.compilerid 
  JOIN dim_layout l ON l.id = v.layoutid 
  JOIN dim_implementation i ON i.id = v.implementationid 
  JOIN dim_query q ON q.id = v.queryid 
  ORDER BY m.id DESC, d.tableschema, q.querytext, c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
{SELECT 
  m.cpu + ' (' + m.cpuarchitecture + ')' 						AS Machine, 
  d.tableschema 											AS [Table schema], 
  q.querytext 												AS [Query], 
  c.compiler 												AS Compiler, 
  c.optlevel 												AS [Opt. level], 
  l.name 													AS [Layout name], 
  CAST(COALESCE(l.chunksize, 'n/a') AS VARCHAR) 			AS [Chunk size (tuples)], 
  IIF(i.templateparam, 'Compile time', 'Runtime') 				AS [Chunk size provided at], 
  IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') 			AS [Chunk sizes considered], 
  runtimes 												AS [Query time] 
  FROM (SELECT machineid, datasetid, queryid, compilerid, layoutid, implementationid, GRUBBS_FILTER(ARRAY(runtime)) as runtimes FROM fact_experiment GROUP BY machineid, datasetid, queryid, compilerid, layoutid, implementationid) AS v 
  JOIN dim_machine m ON m.id = v.machineid 
  JOIN dim_dataset d ON d.id = v.datasetid 
  JOIN dim_compiler c ON c.id = v.compilerid 
  JOIN dim_layout l ON l.id = v.layoutid 
  JOIN dim_implementation i ON i.id = v.implementationid 
  JOIN dim_query q ON q.id = v.queryid 
  ORDER BY m.id DESC, d.tableschema, q.querytext, c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
\vspace*{-5pt}
\caption{The best layouts and most efficient ways of implementing a given query on a given table and executed on a given machine.}  
\label{fig:problem_bests_table}
\vspace{-10pt}
\end{table}
